---
title: "The influence of learning in visual working memory"
author: "William Xiang Quan Ngiam"
fontfamily: times
fontsize: 12pt
output:
  pdf_document: 
    fig_caption: yes
    number_sections: yes
bibliography: ["Thesis References.bib"]
csl: apa.csl
geometry: margin = 1.2in
papersize: a4
header-includes:
- \setlength{\parindent}{3em}   # Controls formatting of paragraph indent
- \setlength{\parskip}{.2em}    # Controls formatting of paragraph skip
- \usepackage{placeins}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \onehalfspacing               # Controls line spacing
- \usepackage{indentfirst}      # Indent first paragraph
- \usepackage{sectsty} 
- \sectionfont{\centering \textbf}
- \subsectionfont{\normalsize}  # Format section and subsection titles
body-includes:
- \setlength{\parident}{3em}
documentclass: "article"
Base Header Level: 2

---
```{r setup, include=FALSE}
library("papaja")
knitr::opts_chunk$set(echo = TRUE)
```

\newpage
\setcounter{tocdepth}{3}
\tableofcontents

\newpage
\pagenumbering{arabic}

\newpage
\addcontentsline{toc}{section}{Chapter 1: Introduction}
\section*{Chapter 1: Introduction}
\setcounter{section}{1}
```{r child = 'Chapter 1.Rmd'}
```

\FloatBarrier
\newpage
\addcontentsline{toc}{section}{Chapter 2: The effect of complexity and familiarity on visual working memory}
\section*{Chapter 2: The effect of complexity and familiarity on visual working memory}
\setcounter{section}{2}
\setcounter{subsection}{0}
```{r child = 'Chapter 2.Rmd'}
```

\FloatBarrier
\newpage
\addcontentsline{toc}{section}{Chapter 3: The effect of statistical learning on visual working memory}
\section*{Chapter 3: The effect of statistical learning on visual working memory}
\setcounter{section}{3}
\setcounter{subsection}{0}
```{r child = 'Chapter 3.Rmd'}
```

\FloatBarrier
\newpage
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

\newpage
\addcontentsline{toc}{section}{List of Tables}
\listoftables

\FloatBarrier
\newpage


#References {-}
\setlength{\parindent}{-0.4in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\noindent